### 2020-09-08 proceedings/tex/figures/ComponentsCompressed/components_compresses.tex
Added proceedings files [skip ci]

\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
\usepackage{tikz}
\usetikzlibrary{calc, positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{matrix}
\usetikzlibrary{shadows}
\usepgflibrary{shapes.misc}
\usepgflibrary{{shapes.geometric}}
\usetikzlibrary{arrows,positioning,shapes}

@@

\tikzset{
    border/.style = { 
        draw, rectangle, minimum width=2.5cm, minimum height=2cm, ultra thick
    },
    pics/Component/.style n args={3}{
        code = {
            \node [border, align=center](-edge){#1};
            \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] ([xshift=-\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {#2}; 
            \draw (-edge.south) node [yshift=-0.75*\mh, align=left, font=\large] {#3};
    }}
    }

\begin{document}
    \begin{tikzpicture}[every node/.style={font={\large}}]
        % Place the blocks 
        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 2cm, row sep = 0.5cm, 
            nodes={anchor=center}]{
        \draw pic (b1) {Component={Source}{t}{$y=g(t)$}};    
        \& 
        \draw pic (b3) {Component={Sink}{t}{}};  
        \&
        \draw pic (b5) {Component={StaticSystem}{t}{$y=g(u, t)$}};    
        \\
        \draw pic (b9) {Component={DiscreteSistem}{k}{$x_{k+1}=f(x_k, u_k, k)$\\$\hspace*{0.4cm}y_k=g(x_k, u_k, k)$}};
        \& 
        \draw pic (b7) {Component={ODESystem}{t}{$\dot{x}=f(x,u,t)$\\$y=g(x,u,t)$}};
        \& 
        \draw pic (b2) {Component={DAESystem}{t}{$0=f(dx,x,u,t)$\\$y=g(x,u,t)$}}; 
        \\
        \draw pic (b4) {Component={RODESystem}{t}{$dx=f(x,u,t,W_t)dt$\\$\hspace*{0.2cm}y=g(x,u,t)$}};
        \& 
        \draw pic (b6) {Component={SDESystem}{t}{$dx=f(x,u,t)dt+h(x,u,t)dW_t$\\$\hspace*{0.2cm}y=g(x,u,t)$}};
        \&
        \draw pic (b8) {Component={DDESystem}{t}{$\dot{x}=f(x,x_\tau,u,t)$\\$y=g(x,u,t)$}}; 
        \\
        };
        % % Glow the blocks
        % \foreach \x in {1, 2, ..., 9}{
        %     \drawshadowbis{b\x-edge};
        % }
        \begin{scope}[line width=\lw, >={Triangle[width=4mm,length=4mm]}]
            \foreach \x in {1, 2, 4, 5, 6, 7, 8, 9}{
                \draw[line width = \lw, ->] (b\x-edge.east) -- ++(1cm, 0cm) node[anchor=west]{$y$};
            }
            \foreach \x in {2, 3, 4, 5, 6, 7, 8, 9}{
                \draw[line width = \lw, ->] ([xshift=-1cm] b\x-edge.west) node[anchor=east]{$u$} -- (b\x-edge.west);
            }
        \end{scope}
    \end{tikzpicture}
\end{document}

>>>>

\documentclass[margin=5mm]{standalone}
\usepackage{tikz}
\usetikzlibrary{calc, positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{matrix}
\usetikzlibrary{shadows}
\usepgflibrary{shapes.misc}
\usepgflibrary{{shapes.geometric}}
\usetikzlibrary{arrows,positioning,shapes}

@@

\tikzset{
    border/.style = { 
        draw, rectangle, minimum width=2.5cm, minimum height=2cm, line width=1.25mm
    },
    pics/Component/.style n args={3}{
        code = {
            \node [border, align=center](-edge){\huge #1};
            \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] ([xshift=-\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {\huge #2}; 
            \draw (-edge.south) node [yshift=-\mh, align=left, font=\huge] {#3};
    }}
    }

\begin{document}
    \begin{tikzpicture}[every node/.style={font={\Large}}]
        % Place the blocks 
        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1cm, row sep = 0.5cm, 
            nodes={anchor=center}]{
        \draw pic (b1) {Component={Source}{t}{$y=g(t)$\\}};    
        \& 
        \draw pic (b3) {Component={Sink}{t}{}};  
        \&
        \draw pic (b5) {Component={StaticSystem}{t}{$y=g(u, t)$}};    
        \\
        \draw pic (b9) {Component={DiscreteSistem}{k}{$x_{k+1}=f(x_k, u_k, k)$\\$\hspace*{0.4cm}y_k=g(x_k, u_k, k)$}};
        \& 
        \draw pic (b7) {Component={ODESystem}{t}{$\dot{x}=f(x,u,t)$\\$y=g(x,u,t)$}};
        \& 
        \draw pic (b2) {Component={DAESystem}{t}{$0=f(dx,x,u,t)$\\$y=g(x,u,t)$}}; 
        \\
        \draw pic (b4) {Component={RODESystem}{t}{$dx=f(x,u,t,W_t)dt$\\$\hspace*{0.2cm}y=g(x,u,t)$}};
        \& 
        \draw pic (b6) {Component={SDESystem}{t}{$dx=f(x,u,t)dt+h(x,u,t)dW_t$\\$\hspace*{0.2cm}y=g(x,u,t)$}};
        \&
        \draw pic (b8) {Component={DDESystem}{t}{$\dot{x}=f(x,x_\tau,u,t)$\\$y=g(x,u,t)$}}; 
        \\
        };
        % % Glow the blocks
        % \foreach \x in {1, 2, ..., 9}{
        %     \drawshadowbis{b\x-edge};
        % }
        \begin{scope}[line width=\lw, >={Triangle[width=4mm,length=4mm]}]
            \foreach \x in {1, 2, 4, 5, 6, 7, 8, 9}{
                \draw[line width = \lw, ->] (b\x-edge.east) -- ++(1cm, 0cm) node[anchor=west]{\huge $y$};
            }
            \foreach \x in {2, 3, 4, 5, 6, 7, 8, 9}{
                \draw[line width = \lw, ->] ([xshift=-1cm] b\x-edge.west) node[anchor=east]{\huge $u$} -- (b\x-edge.west);
            }
        \end{scope}
    \end{tikzpicture}
\end{document}

### 2020-09-08 proceedings/tex/figures/FlowChart/flowchart.tex
Added proceedings files [skip ci]

\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usetikzlibrary{calc, positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{matrix}
\usetikzlibrary{shadows}
\usepgflibrary{shapes.misc}
\usepgflibrary{{shapes.geometric}}
\usetikzlibrary{arrows,positioning,shapes}

@@

\def\lw{1mm}        % Arrow line width
\def\mw{2cm}        % Minimum width of component
\def\mh{1cm}     % Minimum height of component
\def\trianglecoordinate{2mm}    % Starting coordinate clock input triangle of components

@@

\tikzset{
    decisionborder/.style = { 
        draw, diamond,, minimum width=1*\mw, minimum height=\mh, very thick
    },
    pics/Decision/.style ={
        code = {
            \node [decisionborder, align=center](-decisionedge){#1};
    }}
    }

\begin{document}
    \begin{tikzpicture}
        % Place the blocks 
        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 0.75cm, row sep = 1cm, 
            nodes={anchor=center}]{
        \draw pic (b1) {Component={Start}}; \&
        \draw pic (b2) {Decision={Inspect}}; \&
        \draw pic (b3) {Component={Initialize}}; \&
        \draw pic (b4) {Component={Run}}; \&
        \draw pic (b5) {Component={Terminate}}; \\
        };
        \begin{scope}[very thick, >={Triangle[width=2mm,length=2mm]}]
            \draw[->] (b1-edge.east) -- (b2-decisionedge.west);
            \draw[->] (b2-decisionedge.east) -- node[midway, anchor=west, align=center, rotate=90]{Suitable\\For Simulation} (b3-edge.west);
            \draw[->] (b3-edge.east) -- (b4-edge.west);
            \draw[->] (b4-edge.east) -- (b5-edge.west);
            \draw[-] (b2-decisionedge.south) -- node[midway, anchor=east, align=center]{Unsuitable\\For Simulation} ++(0cm, -1cm) coordinate(a);
            \draw[->] (a) -| (b5-edge.south);
        \end{scope}
    \end{tikzpicture}
\end{document}

>>>>

\documentclass[convert={density=900,size=1080x800,outext=.png}, margin=5mm]{standalone}
\usepackage[utf8]{inputenc}
\usepackage{tikz}
\usetikzlibrary{calc, positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{matrix}
\usetikzlibrary{shadows}
\usepgflibrary{shapes.misc}
\usepgflibrary{{shapes.geometric}}
\usetikzlibrary{arrows,positioning,shapes}

@@

\def\lw{1mm}        % Arrow line width
\def\mw{2cm}        % Minimum width of component
\def\mh{0.75cm}     % Minimum height of component
\def\trianglecoordinate{2mm}    % Starting coordinate clock input triangle of components

@@

\tikzset{
    decisionborder/.style = { 
        draw, diamond,, minimum width=\mw, minimum height=0.7*\mh, very thick
    },
    pics/Decision/.style ={
        code = {
            \node [decisionborder, align=center](-decisionedge){#1};
    }}
    }

\begin{document}
    \begin{tikzpicture}
        % Place the blocks 
        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 0.75cm, row sep = 1cm, 
            nodes={anchor=center}]{
        \draw pic (b1) {Component={Start}}; \&
        \draw pic (b2) {Decision={Inspection}}; \&
        \draw pic (b3) {Component={Initialization}}; \&
        \draw pic (b4) {Component={Run}}; \&
        \draw pic (b5) {Component={Termination}}; \\
        };
        \begin{scope}[very thick, >={Triangle[width=2mm,length=2mm]}]
            \draw[->] (b1-edge.east) -- (b2-decisionedge.west);
            \draw[->] (b2-decisionedge.east) -- node[midway, anchor=west, align=center, rotate=90]{Suitable For\\Simulation} (b3-edge.west);
            \draw[->] (b3-edge.east) -- (b4-edge.west);
            \draw[->] (b4-edge.east) -- (b5-edge.west);
            \draw[-] (b2-decisionedge.south) -- node[midway, anchor=east, align=center]{Unsuitable For\\Simulation} ++(0cm, -1cm) coordinate(a);
            \draw[->] (a) -| (b5-edge.south);
        \end{scope}
    \end{tikzpicture}
\end{document}

### 2020-09-08 proceedings/tex/figures/Model/model.tex
Added proceedings files [skip ci]

\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
\usepackage{tikz}

@@

\def\mw{2cm}
\def\mh{1.75cm}
\def\trianglecoordinate{2mm}

@@

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\large}]
        % Place the blocks 
        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1.5cm, row sep = -1cm]{
                                            \& \draw pic (b1) {Component={B1}}; \&                                  \\
        \draw pic (b2) {Component={B2}};    \&                                  \& \draw pic (b3) {Component={B3}}; \\
                                            \& \draw pic (b4) {Component={B4}}; \&                                  \\[1.25cm]
                                            \& \draw pic (b5) {Component={B5}}; \&                                  \\
        };
        % % Glow the blocks
        % \foreach \x in {1, 2, 3, 4, 5}{
        %     \drawshadowbis{b\x-edge};
        % }
        % Draw connections 
        \begin{scope}[line width=2mm, >={Triangle[width=4mm,length=4mm]}]
            \def\shiftamount{0.5mm};
            \draw[-] (b2-edge.east) -- ++(0.5cm, 0cm) coordinate(a);
            \draw[-] (a) -- node[midway, anchor=west]{L1} ++(0, 0.5*\mh) coordinate(b);
            \draw[-] (a) -- node[midway, anchor=west]{L2} ++(0cm, -0.5*\mh) coordinate(c);
            \draw[->] (b) |- (b1-edge.west);
            \draw[->] (c) |- ([yshift=0.25cm] b4-edge.west);
            \draw[-] (b1-edge.east) -- ++(0.4*\mw, 0cm) coordinate(d);
            \draw[-] (b4-edge.east) -- ++(0.4*\mw, 0cm) coordinate(e);
            \draw[-] ([yshift=1mm] d) -- node[midway, anchor=east]{L3} ++(0cm, -0.7*\mh) coordinate(f);
            \draw[-] ([yshift=-1mm] e) -- node[midway, anchor=east]{L4} ++(0cm, 0.7*\mh) coordinate(g);
            \draw[->] ([yshift=\shiftamount] f) |- ([yshift=2mm] b3-edge.west);
            \draw[->] ([yshift=-\shiftamount] g) |- ([yshift=-2mm] b3-edge.west);
            \draw (b5-edge.west) -- ++(-1cm, 0cm) coordinate (h);
            \draw[->] ([yshift=-1mm] h) |- node[midway, anchor=east, yshift=-1.25cm]{L6}  ([yshift=-0.25cm] b4-edge.west);
            \draw[->] ([yshift=1mm] g) |- node[midway, anchor=east, yshift=1.25cm]{L5} (b5-edge.east);
        \end{scope}

        % \Place clock 
        \begin{scope}[shift={(-4.25cm, -4cm)}]
            \draw pic(clk) {Clock={T}} ;
        \end{scope}

        %  Draw rectangle 
        \draw[dashed, thick] ([xshift=-0.25*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=2*\mw, yshift=0.25*\mh] b1-edge.north east);
        \draw (b3-edge.south) node[yshift=-2.75*\mh, xshift=0.4*\mw]{Model};
    \end{tikzpicture}
\end{document}

>>>>

\documentclass[margin=5mm]{standalone}
\usepackage{tikz}

@@

\def\mw{1.5cm}
\def\mh{1cm}
\def\trianglecoordinate{2mm}

@@

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\normalsize}]
        % Place the blocks 
        \matrix (m) [matrix of nodes, ampersand replacement=\&, column sep = 1.5cm, row sep = -0.75cm]{
                                            \& \draw pic (b1) {Component={B1}}; \&                                  \\
        \draw pic (b2) {Component={B2}};    \&                                  \& \draw pic (b3) {Component={B3}}; \\
                                            \& \draw pic (b4) {Component={B4}}; \&                                  \\[0.9cm]
                                            \& \draw pic (b5) {Component={B5}}; \&                                  \\
        };
        % % Glow the blocks
        % \foreach \x in {1, 2, 3, 4, 5}{
        %     \drawshadowbis{b\x-edge};
        % }
        % Draw connections 
        \begin{scope}[line width=1.5mm, >={Triangle[width=3mm,length=2mm]}]
            \def\shiftamount{0.5mm};
            \draw[-] (b2-edge.east) -- ++(0.5cm, 0cm) coordinate(a);
            \draw[-] (a) -- node[midway, anchor=west, yshift=0.25cm]{L1} ++(0, 0.5*\mh) coordinate(b);
            \draw[-] (a) -- node[midway, anchor=west, yshift=-0.1cm]{L2} ++(0cm, -0.5*\mh) coordinate(c);
            \draw[->] (b) |- (b1-edge.west);
            \draw[->] (c) |- ([yshift=0.25cm] b4-edge.west);
            \draw[-] (b1-edge.east) -- ++(0.4*\mw, 0cm) coordinate(d);
            \draw[-] (b4-edge.east) -- ++(0.4*\mw, 0cm) coordinate(e);
            \draw[-] ([yshift=0.75mm] d) -- node[midway, anchor=east, xshift=0.75cm]{L3} ++(0cm, -0.7*\mh) coordinate(f);
            \draw[-] ([yshift=-0.75mm] e) -- node[midway, anchor=east, xshift=0.75cm]{L4} ++(0cm, 0.7*\mh) coordinate(g);
            \draw[->] ([yshift=\shiftamount] f) |- ([yshift=2mm] b3-edge.west);
            \draw[->] ([yshift=-\shiftamount] g) |- ([yshift=-2mm] b3-edge.west);
            \draw (b5-edge.west) -- ++(-1cm, 0cm) coordinate (h);
            \draw[->] ([yshift=-0.75mm] h) |- node[midway, anchor=east, yshift=-0.75cm]{L6}  ([yshift=-0.25cm] b4-edge.west);
            \draw[->] ([yshift=0.75mm] g) |- node[midway, anchor=east, xshift=0.75cm, yshift=0.75cm]{L5} (b5-edge.east);
        \end{scope}

        % \Place clock 
        \begin{scope}[shift={(-4.25cm, -2.25cm)}]
            \draw pic(clk) {Clock={T}} ;
        \end{scope}

        %  Draw rectangle 
        \draw[dashed, thick] ([xshift=-0.25*\mw, yshift=-0.25*\mh] clk-clockedge.south west) rectangle ([xshift=2.25*\mw, yshift=0.25*\mh] b1-edge.north east);
        \draw (b3-edge.south) node[yshift=-2.75*\mh, xshift=0.3*\mw]{model};
    \end{tikzpicture}
\end{document}

### 2020-09-08 proceedings/tex/figures/TaskForComponents/components.tex
Added proceedings files [skip ci]

\documentclass[convert={density=900,size=1080x800,outext=.png}]{standalone}
\usepackage{tikz}
\usetikzlibrary{calc, positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{matrix}
\usetikzlibrary{shadows}
\usepgflibrary{shapes.misc}
\usepgflibrary{{shapes.geometric}}
\usetikzlibrary{arrows,positioning,shapes}

@@

\tikzset{
    border/.style = { 
        draw, rectangle, minimum width=2cm, minimum height=1.5cm, ultra thick
    },
    pics/Component/.style n args = {2}{
        code = {
            \node [border, align=center](-edge){#1};
            \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] ([xshift=-\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {#2}; 
    }}
    }

\begin{document}
    \begin{tikzpicture}
        % Place the blocks 
        \draw pic (b1) {Component={B1}{t}};
        \draw(3.5, 0) pic (b2) {Component={B2}{t}};
        % % Glow the blocks
        % \drawshadowbis{b1-edge};
        % \drawshadowbis{b2-edge};
        \begin{scope}[line width=1.5mm, >={Triangle[width=3mm,length=3mm]}]
            \draw[->] ([xshift=-1cm] b1-edge.west) -- node[midway, anchor=south]{L1} (b1-edge.west);
            \draw[->] (b1-edge.east) -- node[midway, anchor=south]{L2} (b2-edge.west);
            \draw[->] (b2-edge.east) -- node[midway, anchor=south]{L3} ([xshift=1cm] b2-edge.east);
        \end{scope}
    \end{tikzpicture}
\end{document}

>>>>

\documentclass[]{standalone}
\usepackage{tikz}
\usetikzlibrary{calc, positioning}
\usetikzlibrary{arrows.meta}
\usetikzlibrary{matrix}
\usetikzlibrary{shadows}
\usepgflibrary{shapes.misc}
\usepgflibrary{{shapes.geometric}}
\usetikzlibrary{arrows,positioning,shapes}

@@

\tikzset{
    border/.style = { 
        draw, rectangle, minimum width=1.25cm, minimum height=0.75cm, ultra thick
    },
    pics/Component/.style n args = {2}{
        code = {
            \node [border, align=center](-edge){#1};
            \draw[thick] ([xshift=\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] ([xshift=-\trianglecoordinate] -edge.south) -- ([yshift=\trianglecoordinate] -edge.south);
            \draw[thick] (-edge.south) |- ++(-3mm, -4mm) node[xshift=-2mm, yshift=-1mm] {#2}; 
    }}
    }

\begin{document}
    \begin{tikzpicture}
        % Place the blocks 
        \draw pic (b1) {Component={B1}{t}};
        \draw(2.5, 0) pic (b2) {Component={B2}{t}};
        % % Glow the blocks
        % \drawshadowbis{b1-edge};
        % \drawshadowbis{b2-edge};
        \begin{scope}[line width=1.5mm, >={Triangle[width=3mm,length=3mm]}]
            \draw[->] ([xshift=-1cm] b1-edge.west) -- node[midway, anchor=south]{L1} (b1-edge.west);
            \draw[->] (b1-edge.east) -- node[midway, anchor=south]{L2} (b2-edge.west);
            \draw[->] (b2-edge.east) -- node[midway, anchor=south]{L3} ([xshift=1cm] b2-edge.east);
        \end{scope}
    \end{tikzpicture}
\end{document}

### 2020-09-08 proceedings/tex/figures/TaskForComponents/tasks.tex
Added proceedings files [skip ci]

\tikzset{
    border/.style = { 
        draw, circle, minimum width=2cm, thick
    },
    pics/Task/.style={
        code = {
            \node [border, align=center](-edge){#1};
    }}
    }

\begin{document}
    \begin{tikzpicture}[every node/.style={font=\Large}]
        \draw (0, 0) pic (t1) {Task={B1}};
        \draw (2.5, 0) pic (t2) {Task={B1}};
        \draw (6.5, 0) pic (t3) {Task={B2}};
        \draw (9,0) pic (t4) {Task={B2}};
        \begin{scope}[line width = \lw, >={Triangle[width=4mm,length=4mm]}, ->]
            \draw ([xshift=-1.25cm] t1-edge.west) -- node[midway, anchor=south]{L1} (t1-edge.west);
            \draw (t2-edge.east) -- node[midway, anchor=south]{L2}  (t3-edge.west);
            \draw[line width = \lw, ->] (t4-edge.east) -- node[midway, anchor=south]{L3} ([xshift=1cm] t4-edge.east);
        \end{scope}
    \end{tikzpicture}
\end{document}

>>>>

\tikzset{
    border/.style = { 
        draw, circle, minimum width=1cm, ultra thick
    },
    pics/Task/.style={
        code = {
            \node [border, align=center](-edge){#1};
    }}
    }

\begin{document}
    \begin{tikzpicture}
        \draw (0, 0) pic (t1) {Task={B1}};
        \draw (1.5, 0) pic (t2) {Task={B1}};
        \draw (4, 0) pic (t3) {Task={B2}};
        \draw (5.5,0) pic (t4) {Task={B2}};
        \begin{scope}[line width = 1.5mm, >={Triangle[width=3mm,length=3mm]}, ->]
            \draw ([xshift=-1.25cm] t1-edge.west) -- node[midway, anchor=south]{L1} (t1-edge.west);
            \draw (t2-edge.east) -- node[midway, anchor=south]{L2}  (t3-edge.west);
            \draw[->] (t4-edge.east) -- node[midway, anchor=south]{L3} ([xshift=1.25cm] t4-edge.east);
        \end{scope}
    \end{tikzpicture}
\end{document}
